The Array of Long Baseline Antennas for Taking Radio Observations from the Sub-Antarctic

### 2020-10-30 response_to_referee.tex

\noindent \textcolor{blue}{3) Further on the 1-bit quantisation
  approach, would you not only need a better matched antenna but also
  an equalised analogue system to remove the extremely high slope from
  the synchrotron emission at low frequencies. This can be up to 20dB
  at these frequencies. Furthermore, despite talking about 1-bit
  quantisation, as far as I know the plots in the paper are all using
  4 or more bit? Has this been tested in the field or in the lab. I do
  not doubt it will work but it will need careful levelling and
  testing and ideally should be coupled with a noise injection signal
  for calibration.}

In response to both comments above, the SNAP processes the baseband
data using the full resolution of the ADCs (8-bit, with a 14-bit
version possibly in the future) and internally works at 18 bits.  It
is only after channelization that the data are downsampled, so
happily, concerns about cross-channel leakage (either due to RFI,
slopes across the band, antenna performance etc.) aren't affected by
the bit depth at which we save the data.  We have now clarified this
point in section 4.1 of the text and thank the referee for catching
the omission.

\noindent \textcolor{blue}{4) Regarding calibration of this
  instrument, there is virtually no mention of it. This is supposed to
  be a precision cosmology instrument and therefore I would have
  expected some more discussion on calibration. Even if not going down
  the route of an EDGES-style approach, having e.g. a Dicke switch in
  there would allow some measure of the scale and offset.}

First, we stress ALBATROS is not meant to be a precision cosmology
instrument---that will have to wait for future telescope generations.
Dicke switching, at least as part of regular operations, won't add
very much because we can calibrate gain variations off the Galactic
signal.  Each station saves total power autospectra, which have
enormous SNR and are repeated day-to-day.  We find the instrument is
very stable, with RMS gain fluctuations $<$0.6\% over several days,
and typical gain calibration errors of $<$0.04\% on 3-second
timescales based on the Galactic signal.  Any noise offsets will in
general not contribute to cross-correlations and so the chief concern
is to remove them when developing a Galactic model.  PRIZM, which has
several levels of calibration switching, is co-located with ALBATROS,
has similar beams, and operates in a similar frequency range ($>$30
MHz).  We can derive an approximate absolute calibration by comparing
the diurnal variation in Galactic signal (which is insensitive to any
offsets) between PRIZM and ALBATROS.  We have updated the text in
section~5 to reflect these numbers.

@@

\noindent \textcolor{blue}{5) An important aspect of developing an
  autonomous instrument like this is timing. I can see the authors
  have thought about this and discussed it in the paper but have there
  been any experiments of running such systems for months on end and
  analysing the drifts. It seems like something that could be done
  fairly easily in the lab for extended periods of time. If there is
  no data to present on this, then some discussion about such possible
  plans would help.}

Unfortunately all we have are the preliminary lab tests.  The setup
was literally a few pieces of wire hanging off an LWA front end
sitting inside the lab, not even next to a window.  With just a few
minutes of that, we were able to synchronize the EW and NS
polarizations to about 0.1ns.  Our plan was to then go to the roof and
carry out proper tests (exactly the ones the referee suggests), but
unfortunately COVID shut down lab access just a couple of days after
the lab tests.  Similarly, we should have timing information from the
data on disk at Marion, but all science efforts were cancelled during
the 2020 voyage, so we have been unable to retrieve the data.  A
talented undergraduate is doing this work for his thesis, now that
labs are slowly opening back up, but the results will not be ready on
the timescale of resubmission.  We have added text in section 4.1
clarifying that the ORBCOMM and science data are recorded
simultaneously, and we can therefore iteratively improve the timing
calibration in post-processing.  Otherwise we cast ourselves on the
mercy of the journal and the referee to let us defer to a future paper
the analysis we would have loved to have been able to put here.

### 2020-10-30 albatros_paper.tex
HCC final changes!!!!

As a qualitative illustration of the sky signal repeatability,
\autoref{Fig:albatros2_phase} shows the phases of the cross-spectra
binned in local sidereal time.  About 372 hours of data are averaged
into this plot, and no RFI excision has been performed.  A more
detailed analysis of signal repeatability will be presented in a
future paper, but the high signal-to-noise fringe pattern, which is
even visible slightly below $\sim10$~MHz, demonstrates the proof of
concept for building the expanded \albatros\ array.

@@

\begin{figure}[t]
  \begin{center}
    \includegraphics[width=\linewidth]{Figures/baseband_direct_phase_compare.png}
    \caption{Phases from the cross-correlation between two orthogonal
      polarizations from an \albatros\ pathfinder at MARS (see text
      for details).  The top row shows cross-spectrum phases that are
      accumulated directly by the SNAP board, and the bottom row shows
      phases computed from baseband data with 4-bit quantization.  The
      two frequency windows, 5.3--12.6~MHz and 12.6--20.0~MHz, are
      recorded at two separate times, and all waterfall plots are
      shown with 61-kHz resolution.}
    \label{Fig:baseband_direct_phase}
  \end{center}
\end{figure}

>>>>

We can estimate the instrumental gain stability by comparing the total
power between the different days shown in
\autoref{Fig:albatros2_waterfalls}.  We find that the RMS gain
fluctuations between 30 and 40~MHz (where the Galactic signal peaks in
the data) are less than 1\%.  The typical noise on $\sim$3-second time
scales is roughly 0.04\% of the power.  The low noise suggests that
relative calibration, using autospectra recorded by each autonomous
station, can yield sub-percent accuracy.  (Absolute calibration in the
future will be derived by comparing autospectra against \prizm, which
is co-located and absolutely calibrated, or the Global Sky Model.)  As
a qualitative illustration of the sky signal repeatability on smaller
scales, \autoref{Fig:albatros2_phase} shows the phases of the
cross-spectra binned in local sidereal time.  About 372 hours of data
are averaged into this plot, and no RFI excision has been performed.
A more detailed analysis of signal repeatability will be presented in
a future paper, but the high signal-to-noise fringe pattern, which is
even visible slightly below $\sim10$~MHz, demonstrates the proof of
concept for building the expanded \albatros\ array.

@@

\begin{figure}[t]
  \begin{center}
    \includegraphics[width=0.9\linewidth]{Figures/baseband_direct_phase_compare.png}
    \caption{Phases from the cross-correlation between two orthogonal
      polarizations from an \albatros\ pathfinder at MARS (see text
      for details).  The top row shows cross-spectrum phases that are
      accumulated directly by the SNAP board, and the bottom row shows
      phases computed from baseband data with 4-bit quantization.  The
      two frequency windows, 5.3--12.6~MHz and 12.6--20.0~MHz, are
      recorded at two separate times, and all waterfall plots are
      shown with 61-kHz resolution.}
    \label{Fig:baseband_direct_phase}
  \end{center}
\end{figure}
